Too hard to get: the role of probabilistic expectations and cognitive complexity in destructive multi-dimensional reference points

### 2025-03-11 manuscript-apa.qmd

@@

# Methodology

@@

```{r}
#| label: read-in-data
#| include: false

# Source R script used to clean raw data, preferable to reading in exported cleaned data from the script as it preserves the variable types and factor levels

@@

## I. Derivation of first-order conditions for experimental theoretical specification

>>>>

```{r}
#| label: read-in-intermediate-data
#| include: false

# Source R script used to clean raw data, preferable to reading in exported cleaned data from separate R script as this preserves the variable types and factor levels

@@

# Methods

@@

@@

## Derivation of first-order conditions for experimental theoretical specification
